### 2016-09-22 solvers.tex
Add reference to Diophantine supplement

SymPy has equation solvers that can handle ordinary differential
equations, recurrence relationships, Diophantine equations, and algebraic
equations. There is also
rudimentary support for simple partial differential equations.

>>>>

SymPy has equation solvers that can handle ordinary differential
equations, recurrence relationships, Diophantine equations\footnote{See the
  supplementary material for an in depth discussion on the Diophantine submodule.}, and algebraic
equations. There is also
rudimentary support for simple partial differential equations.
